---
title: "Quarto 572 HW"
format: html
editor: visual
---

## Project Beginning

In this project , we have experimented with different quarto settings, and analysed a data set named "Popular Kids"

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
 library(foreign)
 library(ggplot2)
 library(DT)
 setwd(here::here()) 
 dataset=read.arff("PopularKids.arff")
```

You can add options to executable code like this

```{r}
#| echo: false
custom_palette <- c("Sports" = "dodgerblue", "Popular" = "salmon")
ggplot(dataset, aes(x = Goals, y = Grades, fill = Goals)) +
  geom_boxplot() +
  scale_fill_manual(values = custom_palette) +
  labs(title = "Boxplot of Grades by Goals",
       x = "Goals",
       y = "Grades") +
  theme_minimal() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The `echo: false` option disables the printing of code (only output is displayed).

```{r}
result <- kruskal.test(Grades ~ Goals, data = dataset)

# Print the test result
print(result)

means <- aggregate(Grades ~ Goals, data = dataset, FUN = mean)

# Print the means
print(means)

means <- aggregate(. ~ Goals, data = dataset[, c("Goals", "Grades", "Sports", "Looks", "Money")], FUN = mean)
means_rounded <- means
means_rounded[, -1] <- round(means[, -1], digits = 1)
datatable(means_rounded)
```

```{r}

a=table(dataset$Gender,dataset$Goals)
df=as.matrix(a)
colnames(df)
rownames(df)
data_frame=rbind(c("",colnames(df)),c("boy",df[1,1:3]),c("girl",df[2,1:3]))
datatable(data_frame)
```

```{r}


means2 <- aggregate(. ~Gender, data = dataset[, c("Gender", "Grades", "Sports", "Looks", "Money")], FUN = mean)
means_rounded2 <- means2
means_rounded2[, -1] <- round(means2[, -1], digits = 1)
datatable(means_rounded2)
```
